---
title: "Anthro Merge Audit"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "..")
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r load}
library(tidyverse)
anthro_merge <- readRDS("harmonized_outcomes/anthro_merge.rds")
```

## Country coverage

```{r coverage}
anthro_merge %>%
  count(source, country_code, name = "n_children") %>%
  arrange(source, country_code) %>%
  knitr::kable()
```

Total: `r n_distinct(anthro_merge$country_code)` countries, `r nrow(anthro_merge)` children.

## Completeness

```{r completeness}
anthro_merge %>%
  group_by(source, country_code) %>%
  summarise(
    n = n(),
    haz_observed_pct = mean(!is.na(haz)) * 100,
    windex5_observed_pct = mean(!is.na(windex5)) * 100,
    .groups = "drop"
  ) %>%
  knitr::kable(digits = 1)
```

## Household identifier match (ra_anthro countries only)

Share of children whose `hh_id` matched a household-control record
(`urban_rural` present), a proxy for join quality between the anthro
outcome file and the household control file.

```{r id_match}
anthro_merge %>%
  filter(source == "ra_anthro") %>%
  group_by(country_code) %>%
  summarise(n = n(), matched_household_pct = mean(!is.na(urban_rural)) * 100, .groups = "drop") %>%
  knitr::kable(digits = 1)
```

## Outcome prevalence

```{r prevalence}
prevalence <- anthro_merge %>%
  group_by(source, country_code) %>%
  summarise(
    n = n(),
    stunted_pct = mean(stunted, na.rm = TRUE) * 100,
    wasted_pct = mean(wasted, na.rm = TRUE) * 100,
    underweight_pct = mean(underweight, na.rm = TRUE) * 100,
    overweight_pct = mean(overweight, na.rm = TRUE) * 100,
    .groups = "drop"
  )
knitr::kable(prevalence, digits = 1)
```

```{r plot, fig.width=8, fig.height=4}
prevalence %>%
  pivot_longer(ends_with("_pct"), names_to = "outcome", values_to = "pct") %>%
  ggplot(aes(x = reorder(country_code, pct), y = pct, fill = source)) +
  geom_col() +
  facet_wrap(~outcome, scales = "free_y") +
  coord_flip() +
  labs(x = NULL, y = "%") +
  theme_minimal()
```

## Known issues

- Botswana (`bwa`) is excluded entirely from anthropometric outcomes: its
  MICS 2000 export (`hh.sav`, `hl.sav`, `underfive.sav`) has a visit-log
  duplication problem where the same (household, line number) key maps to
  different people's age/sex/HAZ across rows -- 101 of 106 duplicated
  child records in `underfive.sav` disagree on age.
- Namibia (`nam`) has a high anthropometry non-response rate for this DHS
  round: 2,873 of 5,046 children are flagged `HW13 = 7` ("No measurement
  found in HH").
- Trinidad and Tobago (`tto`, from `ra_su26`) has 0 children with an
  observed HAZ -- a pre-existing finding from `ra_su26`'s own pipeline
  review, carried through unchanged in this merge.
